A geometric approach to linear and quadratic Chabauty

### 2020-01-28 MS.tex
Added start using Honda

TODO: explain that the formal group gives the group law on $J(\Z_p)_0$. Explain the logarithm. Prove Theorem~\ref{thm:kappanice}.

>>>>

This formal group tells us exactly how multiplication works on $G(\Z/p^e\Z)_0$; if we let $t = (t_1,\dots,t_d)$ denote the formal parameters giving the isomorphism $\Hat{O}_{G,e} \to \Z_p[[x_1,\dots,x_d]]$, and we represent a point $P$ in $G(\Z/p^e\Z)_0$ by their parameter values $t(P) \in p\Z/p^e\Z$, then the multiplication $p\Z/p^e\Z \times p\Z/p^e\Z \to p\Z/p^e\Z$ is exactly $F$. By taking limits, $F$ also gives the multiplication on $G(\Z_p)_0$.

Now we will look at the theory of formal groups, and how that will help us.  over a $\Q$-algebra, Theorem~1 of \citep{honda70} gives the existence of
